An analysis of interrelations between economic and environmental variables in Australian Winegrowing.

### 2023-10-15 article.tex
added profit to the appendix
added bibliography

\section{Abstract}

Region is a driving force in determining profits.
Fuel and water are the primary driving operational costs

The finding themselves are not that significant, it is the evidence of a complex system governing these relationships that is the significant finding.

They were gathered by Sustainable Winegrowing Australia

What we add is that agricultural economics maybe complex systems that are obfuscated by the expertise of growers to navigate problems such as drought, pests and disease. These systems, although predictable through some variables are not causal. We see this in the evidence of some years not affecting outcomes even though they are known to contain the aforementioned issues.

@@

Historically strong demands for Australian wine have helped to create a thriving industry, however recent pressures brought on by a loss of tourism and labour due to the COVID-19 pandemic, the global freight crisis, war in Europe, tariffs and rising inflation has negatively effected the industry's outlook \citep{wineaustraliaNationalVintageReport2021,wineaustraliaAustralianWineProduction2021}. The 2021-2022 financial year alone saw a decline of 19\% in exports solely due to tariffs \citep{wineaustraliaNationalVintageReport2022}. A greater understanding of the different underlying conditions leading to improved performance in agricultural productivity and sustainability at scale are key to  introducing stronger policy and information to aid in increasing a nations agricultural sustainability \citep{oecdInnovationProductivitySustainability2019}. Specifically within the Australian Wine and vine industry there is a need to further understand the driving relationships between resource use and economic output. Where these relationships can lead to determining better and efficient methods and develop benchmarks with local growers. \citep{lukemanciniUnderstandingAustralianWine2020}
\newline
An unprecedented amount of data regarding the Australian winegrowing industry has been collected through Sustainable Winegrowing Australia, offering new insights into the driving economic forces of the Australian wine industry. This dataset allowed insights into the economic outcome of vineyards through the incorporation of operating costs and grape revenue from grape sales within the data. We use this data to study these economic outcomes and their statistical relationships to vineyards' utilisation of the resources. Answering what the driving factors are behind vineyard economic outcomes, and linking these outcomes to predictor importance. This is done through analysing a new comprehensive nationwide data set using XGBoosted models. We further compare the relationships between different resources to address the extensive collinearity found within the data \citep{chenXGBoostScalableTree2016}. XGBoosted models were used because they are able to overcome multicollinearity as well as highlight the level of importance that predictor variables have on response variables; with importance being able to be statistically defined through multiple methods.

@@

>>>>

@@

Historically strong demands for Australian wine have helped to create a thriving industry, however recent pressures brought on by a loss of tourism and labour due to the COVID-19 pandemic, the global freight crisis, war in Europe, tariffs and rising inflation has negatively effected the industry's outlook \citep{wineaustraliaNationalVintageReport2021,wineaustraliaAustralianWineProduction2021}. The 2021-2022 financial year alone saw a decline of 19\% in exports solely due to tariffs \citep{wineaustraliaNationalVintageReport2022}. A greater understanding of the different underlying conditions leading to improved performance in agricultural productivity and sustainability at scale are key to  introducing stronger policy and information to aid in increasing a nations agricultural sustainability \citep{oecdInnovationProductivitySustainability2019}. Specifically within the Australian Wine and vine industry there is a need to further understand the driving relationships between resource use and economic output. Where these relationships can lead to determining better and efficient methods and develop benchmarks with local growers \citep{lukemanciniUnderstandingAustralianWine2020}.
\par
An unprecedented amount of data regarding the Australian winegrowing industry has been collected through Sustainable Winegrowing Australia, offering new insights into the driving economic forces of the Australian wine industry. This dataset allowed insights into the economic outcome of vineyards through the incorporation of operating costs and grape revenue from grape sales within the data. We use this data to study these economic outcomes and their statistical relationships to vineyards' utilisation of the resources. Answering what the driving factors are behind vineyard economic outcomes, and linking these outcomes to predictor importance. This is done through analysing a new comprehensive nationwide data set using XGBoosted models. We further compare the relationships between different resources to address the extensive collinearity found within the data \citep{chenXGBoostScalableTree2016}. XGBoosted models were used because they are able to overcome multicollinearity as well as highlight the level of importance that predictor variables have on response variables; with importance being able to be statistically defined through multiple methods.

@@

 \subsection{Profit}

\begin{figure} 
  \resizebox{\textwidth}{!}{
  \includegraphics{profit.pdf}}
  \caption{Decision tree predicting revenue. Each node indicates the class predicted, and the proportion of elements agreeing with nodes partitioning, with the left direction indicating a yes to the nodes rule.}\label{fig:revenue_tree}
 \end{figure}

 \begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{profit.png}}
  \caption{The left-hand side depicts the 10 most important variables in predicting revenue using XGBoosted trees as a measure of node occurrence, using a Sankey diagram. The right-hand side depicts the interrelated importance of the ten predictor variables using a chord diagram.}\label{fig:revenue_sankey}
 \end{figure}

Predictions of profit perfomed poorly compared to operating cost and revenue with an average $R^2$ of 0.2535 and standard deviation of 0.3126. With the large standard deviation being indicative of how unstable the models created were.
